---
title: "Notes: Exercise 02a"
author: "Stephen Collins" 
date: "`r format(Sys.time(), '%m.%d.%Y')`"
output: html_document
---
# R Class Notes - (1.21.25 & 1.23.25)

**Bold** *Italicized*

These are instructions for creating bullet points:

- Adding bullet points
- There needs to be a line between main sentence and bullet points
- Another one (DJ Khalid)

Need three slanted ticks in the beginning and {code your working with} to create a code block then at the end three slanted ticks again: 

- It will run the code and then give you the output of the code

``` {code name}

```


Writing code within Rmarkdown example: 
```{r}
 
x <- 6

y <- 8 

z <- x + y

z
```

These are ways that you are able to disable code or results from being displayed in the **HTML** doc: 

- Within the {r <function>} bracket you must include the functions below:
- <include = False> Prevents code and results from appearing
- <echo = FALSE>    Prevents code from appearing
- <message = FALSE> Prevents any messages from appearing
- <warning = FALSE> prevents warnings from appearing 

```{r echo = FALSE}
x <- 6

y <- 8 

z <- x + y

z

```




